\papertitle

### 2021-03-12 source_separation/paper/paper.tex
Add Leo's paragraph on static vs dynamic

	 Orchidea is a framework and set of tools that is currently considered the state-of-the-art for computer-assisted orchestration. Orchidea embeds the target in a feature space and uses a jointly-optimized heuristic and constraint solver to find a combination of samples that best match the target~\cite{Cella18, Cella2020}.

>>>>

	Computer-assisted orchestrations can be divided into two categories: static and dynamic. Static orchestration considers the target as a single vector of timbral features and creates a single onset of note(s) as the solution. Dynamic orchestration considers a time series of features, which allows it to create an orchestration that evolves over time with multiple onsets.

	Orchidea is a framework and set of tools that is currently considered the state-of-the-art for computer-assisted orchestration. It embeds the target in a feature space and uses a jointly-optimized heuristic and constraint solver to find a combination of samples that best match the target~\cite{Cella18, Cella2020}. Orchidea is able to do both static and dynamic orchestration. In order to better observe the effects of source separation, we perform only static orchestrations in this paper. The reasoning for this is that we wish to disentangle the two difficult problems of source separation and time segmentation. By only performing static orchestrations, we reduce the complexity of the problem by removing time segmentation and can better observe the effects of source separation.
